Who introduced the bug? The importance of the previous commit

### 2016-01-21 paperMSR.tex
Modified title, abstract, keywords.

\title{{\ttlit Bug Seeding}, On the importance of Previous Commit}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\maketitle
\begin{abstract}
\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug some , these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit. However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects with present this characteristic.}

\textbf{In this paper, in order to ascertain the validity of such a claim, we have conducted an observational study that involved bug notifications from a very active project such as OpenStack, in which their source code is continuously evolving. Our results are promising in indicating that exists bug fixed which were not introduced in the previous commit.}
\end{abstract}

@@

\keywords{Bug-introduction, SZZ algoritm, Fix-inducing}

>>>>

\title{Who introduced the bug? The importance of the previous commit}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\maketitle
\begin{abstract}
To fix a bug in a certain software product, some parts of its source code are modified. At first glance, it could seem reasonable that the fixed bug was introduced by the previous modification of those same parts of the source code (the previous commit). In fact, many studies on bug seeding start with this assumption. However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug was introduced by other actions, such as an older modification, or a change in called APIs.

This paper tries to shed some light on this area, by analyzing the relationship of bug fixes with their previous commits. To this end, we conducted an observational study on bug reports, their fixes, and their correspoonding previous commits for OpenStack. Our results show that the mentioned asumption does not hold for a large fraction of the analyzed bugs, which were not introduced by their previous commit.
\end{abstract}

@@

\keywords{Bug introduction, bug seeding, SZZ algoritm, previous commit}
